Neural Connectome of the Ctenophore Statocyst

### 2025-06-02 manuscript/Manuscript.qmd
add video legends

![**Figure 4—figure supplement 1**\
(A)...](figures/Figure4_Supplement1.png)

![**supplement video1**\
A...]

![**supplement video2**\
A...]

![**supplement video3**\
A...]

![**supplement video4**\
A...]

![**supplement video5**\
A...]

![**supplement video6**\
A...]

>>>>

![**Figure 4—figure supplement 1.Ciliary beat frequency (CBF) dynamics of balancer cells in additional samples**\
Bar plots showing CBF dynamics of left and right balancers (top and bottom panels, respectively) recorded from the sagittal (A–C) and tentacular (D–F) planes. Positive and negative values indicate opposing sides within each imaging plane. These data correspond to additional samples not shown in the main figure and support the results presented in Figure 4E.](figures/Figure4_Supplement1.png)

![**Video 1.** A...]

![**Video 2.** A...]

![**Video 3.** This video shows high-speed imaging of balancer ciliary beating along with kymographs from two individual balancer cilia. The recording was acquired at 100 frames per second and played back at 30 frames per second (0.3×). The white line overlaid on the kymographs indicates the current time point shown in the video. This example captures a ciliary arrest event in the sagittal plane.]

![**Video 4.**This video shows high-speed imaging of balancer ciliary beating along with kymographs from two individual balancer cilia. The recording was acquired at 100 frames per second and played back at 30 frames per second (0.3×). The white line overlaid on the kymographs indicates the current time point shown in the video. This example captures a ciliary re-beat event in the sagittal plane.]

![**Video 5.** This video shows high-speed imaging of balancer ciliary beating along with kymographs from two individual balancer cilia. The recording was acquired at 100 frames per second and played back at 30 frames per second (0.3×). The white line overlaid on the kymographs indicates the current time point shown in the video. This example captures a ciliary arrest event in the tentacular plane.]

![**Video 6.**This video shows high-speed imaging of balancer ciliary beating along with kymographs from two individual balancer cilia. The recording was acquired at 100 frames per second and played back at 30 frames per second (0.3×). The white line overlaid on the kymographs indicates the current time point shown in the video. This example captures a ciliary re-beat event in the tentacular plane.]
